Security Metrics for the Android Ecosystem

### 2015-07-24 spsm04-thomas.tex
Add citation for the data submission
Reorder sections so that we can make them flow better

@@

\section{Threat model and attack vectors}
\label{sec:threatmodel}

\section{Versions of Android running on devices}\label{sec:da}

@@

\section*{Dataset}
The raw and processed data and source code will be made available where possible when this paper is finalised.
Data from \da\ and \avo\ used in this paper is already available.
The Rwanda and FTSE data cannot be made available due to the terms under which they were obtained.
\todo{We need to submit this data to DSpace and insert a reference.}

>>>>

\section{Threat model}
\label{sec:threatmodel}

@@

\section{Device Analyzer data}\label{sec:da}

@@

\section*{Dataset}
Much of the raw and processed data and source code is available, excluding that which might identify individuals~\cite{Thomas2015e}.
Data from \da\ and \avo\ used in this paper is already available.
The Rwanda and FTSE data cannot be made available due to the terms under which they were obtained.
\todo{We need to submit this data to DSpace and insert a reference.}
